\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-09 poster/main.tex
update plots in poster Objectives.
update plots in poster
some work

\begin{block}{Objectives}
\begin{columns} % Subdivide the first main column
\begin{column}{.62\textwidth}
\begin{enumerate}
\item Designing a differentially private Bayesian inference mechanism.
\item Calibrating mechanism noise by the same probabilistic metric we want to measure accuracy with.
\item Applying smooth sensitivity in mechanism to achieve better accuracy. This is motivated by Fig. \ref{fig_sensitivity} that local sensitivity is very steep in edge but very smooth in center part.
\end{enumerate}
\end{column}
\begin{column}{.35\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.85\textwidth]{poster_0.eps}
\caption{Hellinger Sensitivity}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

\begin{block}{Bayesian Inference Background}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
Conjugate prior distribution, $\betad(\alpha, \beta)$, with hyperparameters $\alpha,\beta\in\mathbb{R}^{+}$;
\begin{itemize}
  \item[-] Observed data set $\dataobs$: $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, $n\in\mathbb{N}$;

  \item[-] Bernoulli likelihood function: $\Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$, where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;

  \item[-] Posterior distribution derived: $\Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$.
\end{itemize}
\end{block}
% and with p.d.f:

@@

In a baseline approach, we sample noise from $Lap(\mu,\nu)$ mechanism, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.

@@

Our approach defines the mechanism $\hexpmech$:

Producing an element $r$ in $\betaset$ with:
$
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = 
\frac 
{exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
$,
given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$.

\begin{itemize}
  \item[-] $\betaset$, the candidates set defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$;

  \item[-] $-\hellinger(\bysinfer(\dataobs),r)$, the scoring function instantiated by Hellinegr distance;

@@

Fig. \ref{fig_sampling} gives the average Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size configuration. In baseline approach (i.e., Laplace mechanism), it is enough to add noise with sensitivity $1$ in 2-dimensional and $2$ in higher dimensional by their equivalence to histogram, giving us the red points in plots. Without the knowledge of equivalence, Laplace usually add noise with sensitivity scale to dimensions, giving us green points. Points in blue are our smoothed Hellinger distance based exponential mechanism.

@@

Fig. \ref{fig_concrete_prob} gives us the concrete probabilities of outputting candidates with certain Hellinegr distance from the correct posterior in 2, 3 and 4 dimensional respectively.
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2-dimensional]{
    \includegraphics[width=0.31\textwidth]{poster_4.eps}
  \label{fig_concrete_prob_2d}
  }
  \subfigure[3-dimensional]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{fig_concrete_prob_3d}
  } 
  \subfigure[4-dimensional]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{fig_concrete_prob_4d}
  } 
\caption{The concrete outputting probabilities under different dimensions with data set of size $600$}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\scriptsize{Two groups of experiments both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}

@@

\begin{itemize}
  \item The smoothed Hellinger distance based exponential mechanism outperforms the $\ell_1$-norm approach when data size growing under the case that Laplace noise doesn't have knowledge of the implicit histogram equivalence.
  % \begin{enumerate}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.

>>>>

\begin{block}{Objectives}
\begin{columns} % Subdivide the first main column
\begin{column}{.69\textwidth}
\begin{enumerate}
\item Designing a differentially private Bayesian inference mechanism.
\item Measuring accuracy with a metric over distributions (Hellinger distance).
\item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
\item Applying smooth sensitivity in mechanism to achieve better accuracy.
        (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
\end{enumerate}
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.85\textwidth]{poster_0.eps}
say something about beta...
\caption{\footnotesize{Local sensitivity of Hellinger}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

\begin{block}{Bayesian inference: Beta-Binomial model}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
%The prior $\betad(\alpha, \beta)$, with hyperparameters $\alpha,\beta\in\mathbb{R}^{+}$ is conjugate to the likelihood function.
\begin{itemize}
  \item[-] Prior on $\theta: \betad(\alpha, \beta), \alpha,\beta\in\mathbb{R}^{+}$, observed data set $\dataobs= (x_1,\dots x_n)\in\{0,1\}^{n}, n\in\mathbb{N}$.

  \item[-] Likelihood function: $\mathbb{L}_{\dataobs | \theta}= \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$, where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;

  \item[-] Posterior distribution over theta: $\mathbb{P}_{\theta|\dataobs}=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$.
\end{itemize}
\end{block}
% and with p.d.f:

@@

In a baseline approach, we sample noise from $Lap(\mu,\nu)$ mechanism, i.e., $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$.
Explain parameters of baseline approach...
\end{block}

@@

Our approach defines the mechanism $\hexpmech$, which outputs  an element $r$ in $\betaset$ with probaiblity:
$
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = 
\frac 
{exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
$

given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$.

\begin{itemize}
  \item[-] $\betaset$, the candidates set defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.

  \item[-] $-\hellinger(\bysinfer(\dataobs),r)$ denotes the scoring function based on the Hellinger distance.

@@

  Fig. \ref{fig_sampling} gives the average Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size configuration.
  In the baseline approach (i.e., Laplace mechanism), it is enough to add noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions since it's equivalent to histogram
  (Should explain better).
  giving us the red points in plots. Without the knowledge of equivalence, Laplace usually add noise with sensitivity scale to dimensions, giving us green points.
  Points in blue are given by the $M_B...$.

@@

Fig. \ref{fig_concrete_prob} gives us the concrete probabilities of outputting candidates with certain Hellinegr distance from the correct posterior in 2, 3 and 4 dimensions respectively.
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2-dimensional]{
    \includegraphics[width=0.31\textwidth]{poster_4.eps}
  \label{fig_concrete_prob_2d}
  }
  \subfigure[3-dimensional]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{fig_concrete_prob_3d}
  } 
  \subfigure[4-dimensional]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{fig_concrete_prob_4d}
  } 
\caption{The concrete outputting probabilities under different dimensions with data set of size $600$}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\scriptsize{Two groups of experiments both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}

@@

\begin{itemize}
\item The smoothed Hellinger distance based exponential mechanism outperforms the asymptotically the baseline 
  approach  when the latter uses a sensitivity proportional to dimensionality.
  (when can this happen?)
  % \begin{enumerate}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.
